Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-24 paper/Draft.tex
Preparing 2 tables for null hypothesis test. FE and RV.

\begin{itemize}

		\item \textbf{New York Fed Survey of Consumer Expectation}
	\begin{itemize}
			\item Include not only perceived probabilities of binary event as in Michigan Survey does, but also elicit densitity forecasts. 
	\end{itemize}
	\item \textbf{Professional Forecasters}

>>>>

Professional Forecasters(SPF) and New York Fed Survey of Consumer Expectation(SCE).

The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both currenct year forecast and 1-year-ahead inflation foreacst each quarter.

SCE data, although each individual is surveyed for 12 months in a row, is only asked to forecast 1-year-ahead inflation. This is especially so in the density forecast. So we can only perform a weak test.

We follow \cite{Manski} to estiamte the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

We drop the outliers of uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
